---
title: "Michigan COVID-19 Mapping"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: yeti
    navbar:
      - {title: explorables, align: right}
      - {title: reports, align: right}
      - {title: publciations, align: right}
      - {title: about us, align: right}
    runtime: shiny
    
---

Home
===================================== 
    
```{r setup, include=FALSE}

library(ggplot2)
library(plotly)
library(plyr)
library(readr)
library(deSolve)

library(flexdashboard)
library (shiny)

load('Workspace2020-04-25-1587832621.RData')

# Convert times to date format for convenience
dates = startdate + ftimes
casedates = startdate + times

lastdate = tail(casedates,1)

# Turn off scientific notation on all axes (set scipen to 0 to enable scientific notation)
options(scipen=999)

# Convert dates from ggplot numeric to plotly numeric
dt = function(dates){as.numeric(as.POSIXct(dates))*1000}
```

Inputs {.sidebar}
-----------------------------------------------------------------------

<a href="#"> Michigan Data </a>

<a href="#"> University of Michigan Data </a>


Row {data-height=300}
-----------------------------------------------------------------------

```{r calcs, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

#Calculate bounds
index= likesample<quantile(likesample,0.95)
ymin = apply(yobsincsample[,index], 1, min)
ymax = apply(yobsincsample[,index], 1, max)
ymed = apply(yobsincsample[,index], 1, median)
deathmin = apply(yobsdeathsample[,index], 1, min)
deathmax = apply(yobsdeathsample[,index], 1, max)
deathmed = apply(yobsdeathsample[,index], 1, median)
ICUmin = apply(ycurrICUsample[,index], 1, min)
ICUmax = apply(ycurrICUsample[,index], 1, max)
ICUmed = apply(ycurrICUsample[,index], 1, median)
O2min = apply(ycurrO2sample[,index], 1, min)
O2max = apply(ycurrO2sample[,index], 1, max)
O2med = apply(ycurrO2sample[,index], 1, median)
patmin = apply(ycurrpatsample[,index], 1, min)
patmax = apply(ycurrpatsample[,index], 1, max)
patmed = apply(ycurrpatsample[,index], 1, median)
ventmin = apply(ycurrventsample[,index], 1, min)
ventmax = apply(ycurrventsample[,index], 1, max)
ventmed = apply(ycurrventsample[,index], 1, median)

xestlh = ode(x0(paramestslh), ftimes, CoVode, paramestslh)

```

### One Week Forecast of COVID-19 Cases in Michigan

<iframe></iframe>

### Three Week Forecast of COVID-19 Cases in Michigan

<iframe></iframe>


Row {data-height=500}
-----------------------------------------------------------------------


### Current Summary

Model forecast for cumulative lab-confirmed cases:

```{r forecasttable}
forecasttable = c()
forecasttable = rbind(forecasttable,
                      c(paste(format(lastdate+7, "%B %e"),'(1 week)'),
                      format(round_any(ymin[(lastdate + 7) - startdate + 1],1), scientific=F),
                      format(round_any(yobscumcarefun(xestlh,paramestslh)[(lastdate + 7) - startdate + 1],1), scientific=F),

                      format(round_any(ymax[(lastdate + 7) - startdate + 1],1), scientific=F) ) )
forecasttable = rbind(forecasttable,
                      c(paste(format(lastdate+21, "%B %e"),'(3 weeks)'),
                      format(round_any(ymin[(lastdate + 21) - startdate + 1],1), scientific=F),
                      format(round_any(yobscumcarefun(xestlh,paramestslh)[(lastdate + 21) - startdate + 1],1), scientific=F),

                      format(round_any(ymax[(lastdate + 21) - startdate + 1],1), scientific=F) ) )
forecasttable = as.data.frame(forecasttable)

colnames(forecasttable) = c("Date", "Uncertainty lower bound", "Best-fit", "Uncertainty upper bound")
knitr::kable(forecasttable)
```

Additionally, the current best fit across model simulations projects (for uncertainty ranges, please see plots):

- `r format(lastdate+7, "%B %e, %Y")` (1 week): roughly `r round_any(ycurrpatfun(xestlh,paramestslh)[(lastdate + 7) - startdate + 1],100)` COVID+ hospitalized patients (beds needed) with roughly `r round_any(ycurrICUfun(xestlh,paramestslh)[(lastdate + 7) - startdate + 1],10)` in ICU
- `r format(lastdate+21, "%B %e, %Y")` (3 weeks): roughly `r round_any(ycurrpatfun(xestlh,paramestslh)[(lastdate + 21) - startdate + 1],100)` COVID+ hospitalized patients (beds needed) with roughly `r round_any(ycurrICUfun(xestlh,paramestslh)[(lastdate + 21) - startdate + 1],10)` in ICU

<p style="font-size: 10pt; font-style: oblique"> Note that the model is a work in progress and being updated as the epidemic progresses. Because we are still making improvements and including new data in the model, these results are highly preliminary and uncertain. The forecasts shown here also do not account for the ongoing changes in social distancing occurring over the coming weeks. For more on social distancing, see the 'Scenarios' tab.</p>

<p style="font-size: 10pt"> For more information about the transmission model and methods, please see the 'About' tab.</p>


<p style="font-size: 10pt">Data is shown as circles and grey shaded regions indicate uncertainty bounds for the best fit 95% across 1000 simulations. Hover over plots to see data values and interactive menu, and scroll down to see additional plots.</p>

*Updated `r format(Sys.time(), "%B %e, %Y at %H:%M %Z")`*



Social Distancing Scenarios
===================================== 

### Social Distancing Scenarios

<iframe id="socialdistancing" src="https://sph-umich.shinyapps.io/covid-19-scenarios/" style="border: none; width: 100%; height: 700px" frameborder="0"></iframe>